---
title: "model_selection.Rmd"
output: html_document
date: "2024-09-20"
---
```{r}
if(!require('PMCMRplus')) {
  install.packages('PMCMRplus')
  library('PMCMRplus')
}
```
Install and load package

```{r}
ThreeVersions <- matrix(c(0.61,0.68,0.71, # F1
                          0.61,0.68,0.71, # Precision
                          0.61,0.68,0.71), # Recall
  nrow = 3,
  byrow = TRUE,
  dimnames = list(1:3,
                  c('Telugu','Mizo','All')
  )
)
```
This is the comparison of the metrics for Chungli Ao + Telugu / Mizo / All. 

```{r}
friedman.test(ThreeVersions)
```
First we do Friedman to see if any model is significantly better than the others
based on these metrics. Note that Friedman requires more than three metrics --
12 would be ideally per Demshar 2006, but 5 would be tolerable. 3 is not great.
Anyway, we find that there is a significant difference.

```{r}
frdAllPairsNemenyiTest(ThreeVersions)
```
Nemenyi tells us which model is significantly different. We find that 'All' is 
significantly better than Telugu, but not significantly better than 'Mizo'. 
'Mizo' is not significantly better than 'Telugu.'